High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-09-11 notebooks/prototyping.qmd
slowly slowly

# Unpack
exp = outcome.exp
model_dict = outcome.model_dict
generator_dict = outcome.generator_dict
bmk = outcome.bmk
```

@@

# Unpack
counterfactual_data = exp.counterfactual_data
X, labels = counterfactual_data.X, counterfactual_data.output_encoder.labels
M = model_dict["MLP"]
gen = filter(((k,v),) -> k in ["ECCCo", "ECCCo-Δ"], generator_dict)

>>>>

# Unpack
exper = outcome.exper
model_dict = outcome.model_dict
generator_dict = outcome.generator_dict
bmk = outcome.bmk
```

@@

# Unpack
counterfactual_data = exper.counterfactual_data
X, labels = counterfactual_data.X, counterfactual_data.output_encoder.labels
M = model_dict["MLP"]
gen = filter(((k,v),) -> k in ["ECCCo", "ECCCo-Δ"], generator_dict)
